\vspace{-15mm} \fontsize{24pt}{10pt}\selectfont \textbf{Traversing symmetric NAT with predictable port allocation function}

### 2013-12-15 paper.tex
some fixes

% ------
% Header/footer
\usepackage{fancyhdr}
	\pagestyle{fancy}
	\fancyhead{}
	\fancyfoot{}
	\fancyhead[C]{Security Protocol Workshop $\bullet$ March 2014 $\bullet$ Vol 1}
	\fancyfoot[RO,LE]{\thepage}

@@

\paragraph{Port restricted cone NAT.} ~\\
Allocation table $\mathbb{AT} \subseteq \{\mathbb{IP}_{in} \times \mathbb{PORT} \times \mathbb{IP}_{ex} \times \mathbb{PORT}\} \times \mathbb{PORT}$ 
holds associations between internal hosts socket, external host socket and mapped external NAT port. 
% Rule is created once the connection from the internal host is initiated to an arbitrary external address.
Filtering rule is:
\begin{align*}
& PASS((\text{IP\textsubscript{out}}, \text{PORT\textsubscript{out}}, \text{IP\textsubscript{nat}}, \text{PORT\textsubscript{nat}} )) \Leftrightarrow \\
&  \exists \; \text{IP\textsubscript{in}} \in \mathbb{IP}, \; \text{PORT\textsubscript{in}} \in \mathbb{PORT}:\\
& ((\text{IP\textsubscript{in}}, \text{PORT\textsubscript{in}}, \text{IP\textsubscript{ex}}, \text{PORT\textsubscript{ex}}), \text{PORT\textsubscript{nat}} ) \in \mathbb{AT}
\end{align*}

@@

\begin{mydef}
\label{def:log}
Algorithm log $\mathcal{L}^A_{\mathcal{A}}$ is a set of tuples $(p_1, p_2, p_3) \in \mathcal{L}^A_{\mathcal{A}}$ produced
by NAT traversal algorithm $\mathcal{A}$ execution on host $A$, where: \\
%$\mathcal{A}(0, s, (\lambda, t_s)) = (p_1, p_2)$ 
%are generated by $\mathcal{A}$ for some parameters $\lambda, t_s$ in some step $s$. The $p_3$ is 
%an allocated port by $NAT^A$ for request $(p_1, p_2)$ in a given step. Algorithm log for host $B$ is defined analogically. 
%Furthermore from our setting the 
%following formula holds:\footnote{From definition of a port sensitive symmetric NAT.} %$\mathcal{L^{A}} \subseteq PORT_{in}^{A} \times PORT_{nat}^{B} \times PORT_{nat}^{A}$,

@@

\begin{mydef}
Baby-step giant-step algorithm
\[
u \in \mathcal{U}, s \in \mathcal{S}: 
\mathcal{A}(u, s) = \begin{dcases*}
         (0, s)  & when $u=0$\\
         (0, 2s) & when $u=1$
        \end{dcases*}
\]
\end{mydef}

@@

\subsection{Algorithm IV -- Poisson sampling}
Algorithm with the best success rate in our simulation is based on sampling Poisson distribution.
The main idea is to let the algorithm simulate the Poisson process that the network of the
other party follows. Duplicates are removed since it does not lead to new port allocation.

>>>>

% ------
% Header/footer
\usepackage{fancyhdr}
	\pagestyle{fancy}
	\fancyhead{}
	\fancyfoot{}
	\fancyhead[C]{SPW 2014 $\bullet$ Twenty-second International Workshop on Security Protocols}
	\fancyfoot[RO,LE]{\thepage}
% CFP: http://www.wikicfp.com/cfp/servlet/event.showcfp?eventid=33620&copyownerid=44118

@@

\paragraph{Port restricted cone NAT.} ~\\
Allocation table $\mathbb{AT} \subseteq \{\mathbb{IP}_{in} \times \mathbb{PORT} \times \mathbb{IP}_{ex} \times \mathbb{PORT}\} \times \mathbb{PORT}$ 
holds associations between internal hosts socket, external host socket and mapped external NAT port. 
% Rule is created once the connection from the internal host is initiated to an arbitrary external address.
Filtering rule is:
\begin{align*}
& PASS((\text{IP\textsubscript{ex}}, \text{PORT\textsubscript{ex}}, \text{IP\textsubscript{nat}}, \text{PORT\textsubscript{nat}} )) \Leftrightarrow \\
&  \exists \; \text{IP\textsubscript{in}} \in \mathbb{IP}, \; \text{PORT\textsubscript{in}} \in \mathbb{PORT}:\\
& ((\text{IP\textsubscript{in}}, \text{PORT\textsubscript{in}}, \text{IP\textsubscript{ex}}, \text{PORT\textsubscript{ex}}), \text{PORT\textsubscript{nat}} ) \in \mathbb{AT}
\end{align*}

@@

\begin{mydef}
\label{def:log}
Algorithm log $\mathcal{L}^A_{\mathcal{A}}$ is a set of tuples $(p_1, p_2, p_3) \in \mathcal{L}^A_{\mathcal{A}}$ produced
by the NAT traversal algorithm $\mathcal{A}$ execution on the host $A$, where: \\
%$\mathcal{A}(0, s, (\lambda, t_s)) = (p_1, p_2)$ 
%are generated by $\mathcal{A}$ for some parameters $\lambda, t_s$ in some step $s$. The $p_3$ is 
%an allocated port by $NAT^A$ for request $(p_1, p_2)$ in a given step. Algorithm log for host $B$ is defined analogically. 
%Furthermore from our setting the 
%following formula holds:\footnote{From definition of a port sensitive symmetric NAT.} %$\mathcal{L^{A}} \subseteq PORT_{in}^{A} \times PORT_{nat}^{B} \times PORT_{nat}^{A}$,

@@

\begin{mydef}
Baby-step giant-step algorithm
\[
u \in \mathcal{U}, s \in \mathcal{S}: 
\mathcal{A}(u, s) = \begin{dcases*}
         (0, s)  & \text{if} $u=0$\\
         (0, 2s) & \text{if} $u=1$
        \end{dcases*}
\]
\end{mydef}

@@

\subsection{Algorithm IV -- Poisson sampling}
Algorithm with the best success rate in our simulation is based on sampling Poisson distribution.
The main idea is to let the algorithm simulate the Poisson process that the network of the
other party follows. Duplicates are removed since it does not lead to a new port allocation.
